---
title       : Data Products
subtitle    : Pitch Presentation
author      : Anwaar Khan
job         : 
framework   : io2012        # {io2012, html5slides, shower, dzslides, ...}
highlighter : highlight.js  # {highlight.js, prettify, highlight}
hitheme     : tomorrow      # 
widgets     : []            # {mathjax, quiz, bootstrap}
mode        : selfcontained # {standalone, draft}
knit        : slidify::knit2slides
---

## Introduction

========================================================
This presentation is part of the Course Project for the Coursera Developing Data Products assignment. There are two parts to this assignment.

We are covering second part in this presentation.

--- .class #id 

## Select the best car for your trip App

========================================================

This app helps you to choose a car for a trip, using the mtcars dataset.

First, you need to inform the distance of your trip and the price of gasoline in your region. 

Second, you can choose some caractheristcs of the cars that you desire: Cylinders, Displacement, Horse Power and Transmission.

--- .class #id 

## Slide With Code

========================================================
The data used in the app comes from the Motor Trend Car Road Tests (mtcars) dataset:

```{r, echo=TRUE}
summary(mtcars)
```

--- .class #id 

## Slide With plot

========================================================
Here we can see the relationship between three variables: miles per gallon (mpg), displacement (disp) and weight (wt).

```{r, echo=TRUE}
library(car)
scatterplot.matrix(~mpg+disp+wt, data=mtcars, cex.axis=1.5)
```
